%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% TeX Gyre Pagella
% \usepackage{tgpagella}
\usepackage{tgpagella,eulervm}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}
{\begin{itemize}[leftmargin=0.05in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\setlength{\footskip}{5pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{website.com}{\Large Name}} & Email : \href{mailto:email}{email}\\
%   \href{website.com/}{website.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Arif Syraj} \\ \vspace{1pt}
  \small 929-271-7864 $|$ \href{mailto:arif.syraj1@gmail.com}{\underline{arif.syraj1@gmail.com}} $|$
  \href{https://linkedin.com/in/arifsyraj}{\underline{linkedin.com/in/arifsyraj}} $|$
  \href{https://github.com/arif-syr}{\underline{github.com/arif-syr}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of San Francisco}{San Francisco, CA}
{Master of Science, Computer Science}{August 2023 -- December 2025}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
        \textbf{Relevant Coursework}{: Principles of Software Development, Foundations of A.I., Systems Programming, Software Development Lifecycle, Cloud Computing}
        }}
\end{itemize}

\resumeSubheading
{University of Illinois at Urbana-Champaign}{Champaign, IL}
{Bachelor of Science, Mechanical Engineering}{August 2016 - May 2021}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
        \textbf{Relevant Coursework}{: Discrete Structures, Data Structures \& Algorithms, Database Systems, Linear Algebra}
        }}
\end{itemize}

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Programming Languages}{: Python, Java, C, C++, JavaScript, HTML5, CSS3, SQL} \\
        \textbf{General}{: Finetuning, Prompt Engineering, Agile, Data Scraping, Shell Scripting, Containerization, Multithreading, CI/CD, Automated Testing, Cloud Deployment} \\
        \textbf{Frameworks/Tools}{: Linux, Docker, ROS, pytorch, tensorflow, MongoDB, React, Node.js, Express, JUnit}
        }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Software Engineer}{March 2021 -- July 2022}
{EarthSense, Inc.}{Champaign, IL}
\resumeItemListStart
\resumeItem{Designed an algorithm to estimate plant height using noisy LiDAR data collected by our phenotyping robot, cutting error by >50\% across datasets over the previous algorithm and beating accuracy of manual measurements.}
\resumeItem{Revamped robot autonomy by designing a crash detection algorithm fusing LiDAR and odometry data collected from various environments, reducing overall false positives and negatives by 75\%.}
\resumeItem{Greatly decreased need for manual waypoint recording by implementing automatic waypoint generation on turns, saving customers several minutes per data collection and improving robot autonomy.}
\resumeItem{Introduced a culture of documentation in our workflows for libraries and testing methodologies, which I later used to onboard interns for a summer.}
\resumeItem{Extensively tested robot system functionality, standardized testing methodologies and created utility shell scripts, helping catch several system bugs before deployment to customers.}

\resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 20XX - Sep 20XX}
%     \resumeItemListStart
%        \resumeItem{Lorem Ipsum}
%          {Lorem Ipsum Lorem Ipsum Lorem Ipsum Lorem Ipsum Lorem Ipsum Lorem Ipsum Lorem Ipsum Lorem Ipsum}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{LLM's To Detect Chart Misinformation} \emph{}}{August 2024}
\resumeItemListStart
\resumeItem{Finetuned a multi-modal LLM to detect visual misinformation in bar charts using LoRA and 2.3k examples.}
\resumeItem{Resulted in a model that can identify visually manipulated bar charts 90\% of the time.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Craigslist Apartment Scraper} \emph{}}{July 2023}
\resumeItemListStart
\resumeItem{A containerized Python web-scraping script that enables a user to browse hundreds of ads for rental accomodation on Craigslist in a fraction of the time it would take to do so using the website.}
\resumeItem{Scraped results are output to HTML files in a readable manner according to a list of user-specified constraints on commute time, rent, number of bedrooms, location, shared versus whole apartments, and more.}
\resumeItem{Allows a user to easily see commute times to a specified location by foot, bike, and car. This data is queried from OpenStreetMap and can be used to sort listings according to travel time buckets by a chosen mode of transport.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Syllabus Generator} \emph{}}{May 2024}
\resumeItemListStart
\resumeItem{Used low-cost LLMs and crewAI to coordinate the automatic generation of a syllabus using basic course info.}
\resumeItem{Implemented prompt engineering techniques to optimize syllabus section generation, significantly improving output quality and relevance.}
\resumeItem{Developed a microservice using FastAPI that talks to large LLM's like ChatGPT for automated syllabus generation.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------AWARDS/RECOGNITION-----------
\section{Awards/Publications}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{University of San Francisco Computer Science Scholarship - Merit Based Award} \emph{}}{May 2023}

\resumeProjectHeading
{\textbf{EnterpriseWorks Top Summer Intern Award} \emph{}}{July 2021}
\resumeItemListStart
\resumeItem{Received a summer intern award in the 'Best Technical Innovation' category by the EnterpriseWorks Incubator.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
